---
title: "Monthly Feedback report"
params:
  name: NA
  month: NA
  data: NA
  data_raw: NA
output:
  html_document: default
---
<style type="text/css">
.main-container {
  max-width: 90%;
  margin-left: auto;
  margin-right: auto;
  text-align: center;
}
</style>

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(lubridate)
library(DT)
library(scales)
knitr::opts_chunk$set(echo = FALSE,fig.height=2,warning = F,message = F)
options(scipen = 999)

prios <- c("1"="1A","2"="1B","3"="2A","4"="2B","5"="3","7"="Referral")

priopal = c("1A" = "#FF0000","1B"="#FFA500","2A"="#FFFF00","2B"="#a5ff00","3"="#66CD00","Referral"="#0000FF")

n_min = 50

sec_to_time <- function(x){
  t <- seconds_to_period(x)
  sprintf('%02d:%02d', minute(t), second(t))
}

data <- params$data %>%
  mutate(me = ifelse(name == params$name,T,F),
         now = ifelse(month == ymd(params$month),T,F),
         last = ifelse(month == ymd(params$month)-months(1),T,F),
         identity = 1) %>%
  filter(n_cn > n_min | me,
         month <= ymd(params$month),
         month > ymd(params$month) - years(1),
         user_org == first(user_org[me]))

plot_line_graph <- function(d,measure,name,x_name="Month",y_name="Value",base = "n_cn", n_min = 50){
  
  meanvals <- d %>%
    group_by(me) %>%
    summarise(measure = round(mean(rep(!!sym(measure), times=!!sym(base)),na.rm = T))) %>%
    pull(measure)
  
  n_max <- max(d[[base]],na.rm = T)
  
  if(y_name == "Minutes"){
    meanvals = sec_to_time(meanvals)
    }
  
  plt <- d %>%
    group_by(month,me) %>%
    summarise(measure = median(!!sym(measure),na.rm = T),
              mq1 = quantile(!!sym(measure),na.rm = T)[2],
              mq3 = quantile(!!sym(measure),na.rm = T)[4],
              # If weighting is not used (identity), consider the measure itself to be the base n value for alpha calculation
              n = ifelse(sum(!!sym(base)) == n(),
                         sum(!!sym(measure)),
                         sum(!!sym(base)))) %>%
    group_by(me) %>%
    mutate(next_n = lag(n)) %>%
  ggplot(aes(x=as.Date(month), 
             y=measure, 
             ymin = mq1,
             ymax = mq3,
             alpha = ifelse(me,
                            rescale(n,c(0.2,1),c(0,n_max)),
                            0.2),
             group = me, 
             label = ifelse(me,round(measure),NA),
             color = ordered(ifelse(me,
                                    paste("Me:",meanvals[2]),
                                    paste("Others:",meanvals[1]))))) +
  geom_ribbon(color = NA, alpha = 0.2) +
  geom_line() + 
  geom_label(show.legend = FALSE) +
  scale_color_manual(values = c("red","black")) + 
  scale_alpha(guide = 'none') +
  scale_x_date(date_minor_breaks = "1 month") +
  guides(colour = guide_legend(override.aes = list(shape = 21)))+
  labs(title = paste(name,"Last month:",round(filter(d,now & me)[measure],1)),
       color = "Whole year",
       y = y_name,
       x = x_name)
  
  if(y_name == "Minutes"){
    plt$layers[[3]] <- NULL
    plt <- plt + 
      geom_label(aes(label = ifelse(me,sec_to_time(round(measure)),NA)),show.legend = FALSE) +
      scale_y_time(labels = function(l) strftime(l, '%M:%S')) +
      labs(title = paste(name,"Last month:",sec_to_time(round(filter(d,now & me)[measure]))))
  }
  return(plt)
  
}

plot_dens_graph <- function(d,measure,name){
  d %>%
  filter(now) %>%
  ggplot(aes(x = !!as.symbol(measure))) +
    geom_density() +
    geom_vline(xintercept = as.numeric(select(filter(d,now,me),!!as.symbol(measure))),color = "red") +
    geom_vline(xintercept = as.numeric(select(filter(d,last,me),!!as.symbol(measure))),color = "red", alpha = 0.2)
}

plot_funnel_graph <- function(d,measure,n,name){
  d %>%
  filter(now) %>%
    ggplot(aes(x=!!as.symbol(n), 
               y=!!as.symbol(measure), 
               alpha = ifelse(me,1,0.2),
               group = name, 
               color = ifelse(me,"red","black"))) +
    geom_point() + 
    scale_color_identity() + 
    theme(legend.position = "none") +
    labs(title = measure)
}

```

The analysis below reports data for `r params$name` during `r paste(month(report_date,label = T),year(report_date))`, together with one year of historical data. Parameters are reported in comparison with the median value for all other call-takers in the region (an interval which covers 50% of all call-takers vaues are denoted by the shaded area). The reliability of the value is reflected by the transparancy of the values, with metrics based on fewer cases being more transparent.

Cohorts refered to in the report include incidents with a __care need__ ,(close reason = Ambulance need, No Ambulance need, Light-care ambulance), and __patient care__ (care need per above as well as being single patient calls assessed with the CDSS). note that the quality of the data may be impacted by missing data, including  __`r round((1-filter(data,me,now)$n_has_close/filter(data,me,now)$n_total)*100)`%__ of incident mising a close reason, __`r round((1-filter(data,me,now)$n_matched_call/filter(data,me,now)$n_total)*100)`%__ incidents missing a link to an incoming phone call, and __`r round((1-filter(data,me,now)$n_pc_pnr/filter(data,me,now)$n_pc)*100)`%__ of patient care incidents missing a valid personal idntification number.

The statistics are reported in two parts. The first __descriptive__ part includes measures where high or low values are not considered good or bad. The second part reports __quality measures__ where it is desireable to have a high or low value. Finally, a __table__ of individual incidents is provided where you can review data about your individual calls.

If you have questions or requests regarding the contents of the reports, or to report incorrect data, please contact douglas.spangler@akademiska.se.

# Descriptive data
```{r volym}
plot_line_graph(data,"n_cn","Number of calls with care need",y_name = "Number",base = "identity")
```
<br>
Total number of cases with care need per month
<br><br><br><br>
```{r pct_hanv}
plot_line_graph(data,"pct_cn_referral","Percent referred",y_name = "Percent",base = "n_cn")
```
<br>
Proportion of all incidents involving a medical problem who did not receive an ambulance response.
<br><br><br><br>
```{r pct p1}
plot_line_graph(data,"pct_cn_p1","Percent priority 1",y_name = "Percent",base = "n_cn")
```
<br>
Proportion of all incidents  involving a medical problem receiving a priority 1 (lights and sirens) response.
<br><br><br><br>
```{r Samtalstid}
plot_line_graph(data,"median_call_time","Median call time",y_name = "Minutes",base = "n_matched_call")
```
<br>
Median time from answering to ending the first call associated with all incidents.
<br><br><br><br>
```{r prio_up}
plot_line_graph(data,"pct_pc_mbs_up","Percent manually upgraded patients",y_name = "Percent",base = "n_pc")
```
<br>
Proportion of all single patient incidents where the response priority was higher than that suggested by the CDSS.
<br><br><br><br>
```{r prio_ner}
plot_line_graph(data,"pct_pc_mbs_down","Percent manually downgraded patients",y_name = "Percent",base = "n_pc")
```
<br>
Proportion of all single patient incidents where the response priority was lower than that suggested by the CDSS.
<br><br><br><br>
```{r cats,fig.height=4,fig.width = 10}
params$data_raw %>%
  group_by(`Call type`,`Chosen priority`) %>%
  summarise(Count = n()) %>%
  group_by(`Call type`) %>%
  mutate(n_tot = sum(Count)) %>%
  ggplot(aes(x=reorder(`Call type`,-n_tot),y=Count,fill=`Chosen priority`)) +
  geom_bar(position="stack", stat="identity") +
  scale_fill_manual(values = priopal) +
  theme(axis.text.x = element_text(angle= -45,hjust = 0)) +
  labs(title = "Number of incidents with care need per call type/priority in the last month", x="")
```

<br><br><br><br>

# Quality meaures

```{r Percentdba}
plot_line_graph(data,"pct_pc_dba","Percent patients with life threat questions",y_name = "Percent",base = "n_pc")
```
<br>
Proportion of single patient incidents with initial questions intended to exclude life threatening conditions completed (Breathing/Airway clear/Conscious).
<br><br><br><br>
```{r Percentsokorsak}
plot_line_graph(data,"pct_pc_cat","Percent patients with contact reason",y_name = "Percent",base = "n_pc")
```
<br>
Proportion of single patient incidents with a documented reason for contact in the CDSS.
<br><br><br><br>
```{r Percentkomplett}
plot_line_graph(data,"pct_pc_complete","Percent patients with complete journal",y_name = "Percent",base = "n_pc")
```

<br>
Proportion of single patient incidents in which all parts of the CDSS was completed.
<br><br><br><br>
```{r svarstid}
plot_line_graph(data,"median_queue_time","Median queue time",y_name = "Minutes",base = "n_matched_call")
```

<br>
Median time from receipt of call at the EMD center to answering the first call associated with all incidents.
<br><br><br><br>
```{r larmtid1a}
plot_line_graph(data,"median_p1a_ready_time","Median dispatch time priority 1A
",y_name = "Minutes",base = "n_p1a")
```
<br>
Median time from answering the call to the first of: Marking the call as ready for dispatch, connecting a dispatcher to the call to handle ambulance dispatch, actual ambulance dispatch for Priority 1A (immediately life threatening) incidents.
<br><br><br><br>
```{r larmtid1b}
plot_line_graph(data,"median_p1b_ready_time","Median dispatch time priority 1B",y_name = "Minutes",base = "n_p1b")
```
<br>
Same as above for priority 1B (Emergency, non-life threatening) incidents.
<br><br><br><br>
```{r prio ut-in}
plot_line_graph(data,"pct_p2out_p1in","Percent priority 2 patients transported priority 1",y_name = "Percent",base = "n_p2")
```
<br>
Proportion of incidents dispatched as priority 2A or B which were subsequently transported by the ambulance on scene to a hospital with lights and sirens. A measure of under-triage.
<br><br><br><br>
```{r prio_ut-vpp}
plot_line_graph(data,"pct_p1out_vpp","Percent priority 1 patients not transported (with exceptions)",y_name = "Percent",base = "n_p1")
```
<br>
Proportion of incidents dispatched as priority 1A or B which were treated on scene and not transported to a hospital (excluding call types considered to be appropriately treatable on scene: Cardiac Arrest, Allergic reaction, Low blood sugar, Breathing difficulty in children 5 or under). A measure of over-triage.
<br><br><br><br>
```{r hanv}
plot_line_graph(data,"pct_pc_referral_72txp","Percent referred patients transported within 72hrs",y_name = "Percent",base = "n_pc_referral")
```
<br>
Proportion of single patient incidents referred to non-ambulance care where the patient subsequently re-contacted the EMD center within 72 hours and was transported to the hospital. A measure of under-triage.
<br><br><br><br>

# Last months incidents:
```{r raw}
datatable(params$data_raw,rownames = F,options = list(autoWidth = TRUE))
```
